Overview

### 2019-03-16 notebooks/general_info.Rmd
added per-package tally, and a size metric to start off with. looks like the top packages we looked at (with a rudimentary notion of polymorphism size) are plotmo, photobiology, phylosim, imager, IsoplotR, and ggplot2. lots of plotters
coinciding up and running, will generalize the function next. gonna look into other occurences of char/real that are unexplained by coinciding list signatures

>>>>

Alright, let's do a package tally for all packages.
First, let's make all the classes primitive in our previous collapsed list.

```{r}
los_basic_no_null_real_primitive_class <- lapply(los_basic_no_null_real, function(lof) {lapply(lof, class_to_primitive_df)})
```

Note: this takes a long time to run.
```{r}
all_tallies_all_reduced <- lapply(los_basic_no_null_real_primitive_class, tally_up_lofun_c)
```

```{r}
all_tallies_sizes <- lapply(all_tallies_all_reduced, function(x) x$tot_size_of_poly)
```

Ok.
It's certainly not perfect, but one metric I used for figuring out the size of polymorphism is just by summing up the type-, attribute-, and class-based polymorphism of each argument in a function.
This might give us some leads.
The top 20 polymorphic packages by this metric is:

```{r}
head(sort(unlist(all_tallies_sizes), decreasing=TRUE), 20)
```

Ok.
Let's see what we can get out of coinciding type signatures.
With out reduced type system, we might want to know a little bit more about the "real", "character" type signature, which is by far one of the most common signatures.
We hypothesize that these should appear alongside lists (and possibly vectors).
For lists only, we can do this easily:
```{r}
# for list coinciding
coincide_list_index <- get_fun_sigs_matching_pred_from_lopkg(los_basic_no_null_real_primitive_class, does_df_have_coinciding_types_index_and_list_reduced_TS)

# just real, character
char_real_sigs <- get_fun_sigs_matching_pred_from_lopkg(los_basic_no_null_real_primitive_class, does_df_have_X_types, types_to_find=c("real", "character"), strict=TRUE)
```

Let's look for vectors, also.
```{r}
coincide_list_vector_index <- get_fun_sigs_matching_pred_from_lopkg(los, does_df_have_coinciding_types_index_and_list_or_vector)
```
